---
title: "First Results: Skill Building and Self-Acceptance as Mechanisms of Positive Personality Change"
author: "Michael Krämer"
toc: true
toc-depth: 5
toc-title: Contents
number-sections: true
format:
#  docx:
#    highlight-style: github
  html:
    link-external-icon: true
    link-external-newwindow: true
    code-block-bg: true
    code-block-border-left: "#31BAE9"
#comments:
#  hypothesis: true
editor: source
#bibliography: references-zotero.bib
#csl: apa.csl
---
<!--
You can find the preregistration [here](https://osf.io/4syhg).
-->

## Load packages

```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
library(renv)
library(tidyverse)
library(labelled)
library(psych)
library(GPArotation)
#library(devtools)
#install_github("cran/multicon") # not on CRAN atm
library(multicon)
library(correlation)
library(corrplot)
library(lavaan)
```

## Data cleaning

```{r}
#| echo: true
#| warning: false
#| output: false
#| code-fold: true
#| code-summary: "Show the code"
source("clean_data.R")
```

## Confirmatory results

### Hypothesis 1: Well-Being - Similarity Correlations {#hyp1}

*All four psychological well-being indicators will be positively correlated with a greater similarity between current- and ideal self-ratings of personality.* 

To examine this at the level of overall profiles, we will compute the correlations between the psychological well-being indicators and the Fisher z transformed correlations between the facet- and item-level real-ideal self-profiles. To examine this at the level of individual traits, we will compute the correlation between psychological well-being indicators and the squared difference between current- and ideal-self rating for each Big Five trait and facet. 

#### Profile similarity

Computations:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true

cormat_profile <- cor(df_sbsa[, c("swls", "meaning", "selfes", "concept",
                                  "profile_corr_item_z", "profile_corr_facet_z")], use = "pairwise.complete.obs")

rownames(cormat_profile) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                              "Item-Level Profile Corr (z)", "Facet-Level Profile Corr (z)")
colnames(cormat_profile) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                              "Item-Level Profile Corr (z)", "Facet-Level Profile Corr (z)")

```

```{r}
#| echo: true
corrplot(cormat_profile, type = "lower", order = "original", tl.col = "black", tl.srt = 10,
                      addCoef.col ='black', number.cex = 0.7, diag = FALSE) # also add numbers
```

::: {.callout-note appearance="minimal"}
Positive correlations of well-being indicators with profile similarity between current self and ideal self personality. Especially high correlation with self-esteem. High congruence of item-level and facet-level profile similarity.
:::

#### Individual traits: squared differences

Computations:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true

cormat_sqtraits <- cor(df_sbsa[, c("swls", "meaning", "selfes", "concept",
                                   paste0(str_trunc(names(b5_vars)[1:5], 5, ellipsis = ""), "_sqdiff"))], 
                       use = "pairwise.complete.obs")

rownames(cormat_sqtraits) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                               str_to_title(names(b5_vars)[1:5]))
colnames(cormat_sqtraits) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                               str_to_title(names(b5_vars)[1:5]))

cormat_sqfacets <- cor(df_sbsa[, c("swls", "meaning", "selfes", "concept",
                                   paste0(str_trunc(names(b5_vars)[6:20], 5, ellipsis = ""), "_sqdiff"))], 
                       use = "pairwise.complete.obs")

rownames(cormat_sqfacets) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                               str_to_title(names(b5_vars)[6:20]))
colnames(cormat_sqfacets) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                               str_to_title(names(b5_vars)[6:20]))
```

Big Five traits
```{r}
#| echo: true
corrplot(cormat_sqtraits, type = "lower", order = "original", tl.col = "black", tl.srt = 10,
         addCoef.col ='black', number.cex = 0.7, diag = FALSE) # also add numbers
```

Big Five facets
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5
corrplot(cormat_sqfacets, type = "lower", order = "original", tl.col = "black", tl.srt = 10,
         addCoef.col ='black', number.cex = 0.6, diag = FALSE) # also add numbers
```

::: {.callout-note appearance="minimal"}
Here we see negative correlations of well-being indicators with squared trait- and facet-level mean-score differences between current self and ideal self personality.
:::

------------------------------------------------------------------------

### Hypothesis 2: Well-Being - Similarity Correlations {#hyp1}

*Both groups will increase in all four psychological well-being indicators.* 

We will test the mean-level difference between baseline and follow up using a latent change model.

#### Life Satisfaction

Model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true


```



<!--
## References

::: {#refs}
:::
-->