---
title: "First Results: Skill Building and Self-Acceptance as Mechanisms of Positive Personality Change"
author: "Michael Krämer"
toc: true
toc-depth: 5
toc-title: Contents
number-sections: true
format:
#  docx:
#    highlight-style: github
  html:
    link-external-icon: true
    link-external-newwindow: true
    code-block-bg: true
    code-block-border-left: "#31BAE9"
#comments:
#  hypothesis: true
editor: source
#bibliography: references-zotero.bib
#csl: apa.csl
---
<!--
You can find the preregistration [here](https://osf.io/4syhg).
-->

## Load packages

```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
library(renv)
library(tidyverse)
library(broom)
library(labelled)
library(psych)
library(GPArotation)
#library(devtools)
#install_github("cran/multicon") # not on CRAN atm
library(multicon)
library(correlation)
library(corrplot)
library(lavaan)
library(semTools)
library(semPlot)
library(knitr)
library(ggdist)
library(ggforce)
library(nortest)
```

## Data cleaning

```{r}
#| echo: true
#| warning: false
#| output: false
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true
source("clean_data.R")
```

## Confirmatory results

### Hypothesis 1: Well-being - similarity correlations {#hyp1}

*All four psychological well-being indicators will be positively correlated with a greater similarity between current- and ideal self-ratings of personality.* 

To examine this at the level of overall profiles, we will compute the correlations between the psychological well-being indicators and the Fisher z transformed correlations between the facet- and item-level real-ideal self-profiles. To examine this at the level of individual traits, we will compute the correlation between psychological well-being indicators and the squared difference between current- and ideal-self rating for each Big Five trait and facet. 

#### Profile similarity

Computations:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"

cormat_profile <- cor(df_sbsa[, c("swls", "meaning", "selfes", "concept",
                                  "profile_corr_item_z", "profile_corr_facet_z")], use = "pairwise.complete.obs")

rownames(cormat_profile) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                              "Item-Level Profile Corr (z)", "Facet-Level Profile Corr (z)")
colnames(cormat_profile) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                              "Item-Level Profile Corr (z)", "Facet-Level Profile Corr (z)")

```

```{r}
#| echo: true
corrplot(cormat_profile, type = "lower", order = "original", tl.col = "black", tl.srt = 10,
                      addCoef.col ='black', number.cex = 0.7, diag = FALSE) # also add numbers
```

::: {.callout-note appearance="minimal"}
Positive correlations of well-being indicators with profile similarity between current self and ideal self personality. Especially high correlation with self-esteem. High congruence of item-level and facet-level profile similarity.
:::

#### Individual traits: squared differences

Computations:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"

cormat_sqtraits <- cor(df_sbsa[, c("swls", "meaning", "selfes", "concept",
                                   paste0(str_trunc(names(b5_vars)[1:5], 5, ellipsis = ""), "_sqdiff"))], 
                       use = "pairwise.complete.obs")

rownames(cormat_sqtraits) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                               str_to_title(names(b5_vars)[1:5]))
colnames(cormat_sqtraits) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                               str_to_title(names(b5_vars)[1:5]))

cormat_sqfacets <- cor(df_sbsa[, c("swls", "meaning", "selfes", "concept",
                                   paste0(str_trunc(names(b5_vars)[6:20], 5, ellipsis = ""), "_sqdiff"))], 
                       use = "pairwise.complete.obs")

rownames(cormat_sqfacets) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                               str_to_title(names(b5_vars)[6:20]))
colnames(cormat_sqfacets) <- c("Life Satisfaction", "Meaning in Life", "Self-Esteem" , "Self Concept Clarity", 
                               str_to_title(names(b5_vars)[6:20]))
```

Big Five traits
```{r}
#| echo: true
corrplot(cormat_sqtraits, type = "lower", order = "original", tl.col = "black", tl.srt = 10,
         addCoef.col ='black', number.cex = 0.7, diag = FALSE) # also add numbers
```

Big Five facets
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5
corrplot(cormat_sqfacets, type = "lower", order = "original", tl.col = "black", tl.srt = 10,
         addCoef.col ='black', number.cex = 0.6, diag = FALSE) # also add numbers
```

::: {.callout-note appearance="minimal"}
Here we see negative correlations of well-being indicators with squared trait- and facet-level mean-score differences between current self and ideal self personality.
:::

------------------------------------------------------------------------

### Measurement invariance: Well-being indicators {#hyp1}

Testing for measurement invariance of the latent traits across time.

Reshape well-being data:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false

df_sbsa_wide_wb <- df_sbsa %>% 
  arrange(pid, time) %>% 
  select(pid, time, starts_with(c("sw06", "ml01", "rs01", "sc01"))) %>% 
  pivot_wider(names_from = time,
              names_sep = "_t",
              values_from = starts_with(c("sw06", "ml01", "rs01", "sc01")))
colnames(df_sbsa_wide_wb)
```

#### Life satisfaction

Fit model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false
#| cache: true

# Code snippets adapted from https://quantdev.ssri.psu.edu/sites/qdev/files/LongitudinalMeasurementInvariance_2017_1108.html

# Configural invariance model
configural_swls <- '
# Define the latent factors
swls1 =~ NA*sw06_01_t1 + lambda1*sw06_01_t1 + sw06_02_t1 + sw06_03_t1 + sw06_04_t1 + sw06_05_t1 
swls2 =~ NA*sw06_01_t2 + lambda1*sw06_01_t2 + sw06_02_t2 + sw06_03_t2 + sw06_04_t2 + sw06_05_t2

# Intercepts
sw06_01_t1 ~ i1*1
sw06_02_t1 ~ 1
sw06_03_t1 ~ 1
sw06_04_t1 ~ 1
sw06_05_t1 ~ 1

sw06_01_t2 ~ i1*1
sw06_02_t2 ~ 1
sw06_03_t2 ~ 1
sw06_04_t2 ~ 1
sw06_05_t2 ~ 1

# Unique Variances
sw06_01_t1 ~~ sw06_01_t1
sw06_02_t1 ~~ sw06_02_t1
sw06_03_t1 ~~ sw06_03_t1
sw06_04_t1 ~~ sw06_04_t1
sw06_05_t1 ~~ sw06_05_t1

sw06_01_t2 ~~ sw06_01_t2
sw06_02_t2 ~~ sw06_02_t2
sw06_03_t2 ~~ sw06_03_t2
sw06_04_t2 ~~ sw06_04_t2
sw06_05_t2 ~~ sw06_05_t2

# Latent Variable Means
swls1 ~ 0*1
swls2 ~ 1

# Latent Variable Variances and Covariance
swls1 ~~ 1*swls1
swls2 ~~ swls2
swls1 ~~ swls2
'
fit_configural_swls <- cfa(configural_swls, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_configural_swls, fit.measures = TRUE)

# Weak invariance model
weak_swls <- '
# Define the latent factors
swls1 =~ NA*sw06_01_t1 + lambda1*sw06_01_t1 + lambda2*sw06_02_t1 + lambda3*sw06_03_t1 + lambda4*sw06_04_t1 + lambda5*sw06_05_t1 
swls2 =~ NA*sw06_01_t2 + lambda1*sw06_01_t2 + lambda2*sw06_02_t2 + lambda3*sw06_03_t2 + lambda4*sw06_04_t2 + lambda5*sw06_05_t2

# Intercepts
sw06_01_t1 ~ i1*1
sw06_02_t1 ~ 1
sw06_03_t1 ~ 1
sw06_04_t1 ~ 1
sw06_05_t1 ~ 1

sw06_01_t2 ~ i1*1
sw06_02_t2 ~ 1
sw06_03_t2 ~ 1
sw06_04_t2 ~ 1
sw06_05_t2 ~ 1

# Unique Variances
sw06_01_t1 ~~ sw06_01_t1
sw06_02_t1 ~~ sw06_02_t1
sw06_03_t1 ~~ sw06_03_t1
sw06_04_t1 ~~ sw06_04_t1
sw06_05_t1 ~~ sw06_05_t1

sw06_01_t2 ~~ sw06_01_t2
sw06_02_t2 ~~ sw06_02_t2
sw06_03_t2 ~~ sw06_03_t2
sw06_04_t2 ~~ sw06_04_t2
sw06_05_t2 ~~ sw06_05_t2

# Latent Variable Means
swls1 ~ 0*1
swls2 ~ 1

# Latent Variable Variances and Covariance
swls1 ~~ 1*swls1
swls2 ~~ swls2
swls1 ~~ swls2
'
fit_weak_swls <- cfa(weak_swls, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_weak_swls, fit.measures = TRUE)

# Strong invariance model (additional constraints on manifest intercepts)
strong_swls <- '
# Define the latent factors
swls1 =~ NA*sw06_01_t1 + lambda1*sw06_01_t1 + lambda2*sw06_02_t1 + lambda3*sw06_03_t1 + lambda4*sw06_04_t1 + lambda5*sw06_05_t1 
swls2 =~ NA*sw06_01_t2 + lambda1*sw06_01_t2 + lambda2*sw06_02_t2 + lambda3*sw06_03_t2 + lambda4*sw06_04_t2 + lambda5*sw06_05_t2

# Intercepts
sw06_01_t1 ~ i1*1
sw06_02_t1 ~ i2*1
sw06_03_t1 ~ i3*1
sw06_04_t1 ~ i4*1
sw06_05_t1 ~ i5*1

sw06_01_t2 ~ i1*1
sw06_02_t2 ~ i2*1
sw06_03_t2 ~ i3*1
sw06_04_t2 ~ i4*1
sw06_05_t2 ~ i5*1

# Unique Variances
sw06_01_t1 ~~ sw06_01_t1
sw06_02_t1 ~~ sw06_02_t1
sw06_03_t1 ~~ sw06_03_t1
sw06_04_t1 ~~ sw06_04_t1
sw06_05_t1 ~~ sw06_05_t1

sw06_01_t2 ~~ sw06_01_t2
sw06_02_t2 ~~ sw06_02_t2
sw06_03_t2 ~~ sw06_03_t2
sw06_04_t2 ~~ sw06_04_t2
sw06_05_t2 ~~ sw06_05_t2

# Latent Variable Means
swls1 ~ 0*1
swls2 ~ 1

# Latent Variable Variances and Covariance
swls1 ~~ 1*swls1
swls2 ~~ swls2
swls1 ~~ swls2
'
fit_strong_swls <- cfa(strong_swls, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_strong_swls, fit.measures = TRUE)

# Strict invariance model (additional constraints on manifest variances)
strict_swls <- '
# Define the latent factors
swls1 =~ NA*sw06_01_t1 + lambda1*sw06_01_t1 + lambda2*sw06_02_t1 + lambda3*sw06_03_t1 + lambda4*sw06_04_t1 + lambda5*sw06_05_t1 
swls2 =~ NA*sw06_01_t2 + lambda1*sw06_01_t2 + lambda2*sw06_02_t2 + lambda3*sw06_03_t2 + lambda4*sw06_04_t2 + lambda5*sw06_05_t2

# Intercepts
sw06_01_t1 ~ i1*1
sw06_02_t1 ~ i2*1
sw06_03_t1 ~ i3*1
sw06_04_t1 ~ i4*1
sw06_05_t1 ~ i5*1

sw06_01_t2 ~ i1*1
sw06_02_t2 ~ i2*1
sw06_03_t2 ~ i3*1
sw06_04_t2 ~ i4*1
sw06_05_t2 ~ i5*1

# Unique Variances
sw06_01_t1 ~~ u1*sw06_01_t1
sw06_02_t1 ~~ u2*sw06_02_t1
sw06_03_t1 ~~ u3*sw06_03_t1
sw06_04_t1 ~~ u4*sw06_04_t1
sw06_05_t1 ~~ u5*sw06_05_t1

sw06_01_t2 ~~ u1*sw06_01_t2
sw06_02_t2 ~~ u2*sw06_02_t2
sw06_03_t2 ~~ u3*sw06_03_t2
sw06_04_t2 ~~ u4*sw06_04_t2
sw06_05_t2 ~~ u5*sw06_05_t2

# Latent Variable Means
swls1 ~ 0*1
swls2 ~ 1

# Latent Variable Variances and Covariance
swls1 ~~ 1*swls1
swls2 ~~ swls2
swls1 ~~ swls2
'
fit_strict_swls <- cfa(strict_swls, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_strict_swls, fit.measures = TRUE)
```

Results summary:
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5

# compare model fit
bind_rows(broom::glance(fit_configural_swls) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_weak_swls) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_strong_swls) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_strict_swls) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr)) %>% 
  mutate(model = c("configural", "weak", "strong", "strict")) %>% 
  select(model, everything())

# chi-square difference test for nested models 
anova(fit_configural_swls, fit_weak_swls)

anova(fit_weak_swls, fit_strong_swls)

anova(fit_strong_swls, fit_strict_swls)
```

::: {.callout-note appearance="minimal"}
Model fit relatively similar across model specifications. Chi^2 tests indicate that strong measurement invariance is given.
:::

#### Meaning in life

Fit model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false
#| cache: true

# Code snippets adapted from https://quantdev.ssri.psu.edu/sites/qdev/files/LongitudinalMeasurementInvariance_2017_1108.html

# Configural invariance model
configural_meaning <- '
# Define the latent factors
meaning1 =~ NA*ml01_01_t1 + lambda1*ml01_01_t1 + ml01_02_t1 + ml01_03_t1 + ml01_04_t1 + ml01_05_t1 + ml01_06_t1 + ml01_07_t1 + ml01_08_t1 + ml01_09_t1 + ml01_10_t1
meaning2 =~ NA*ml01_01_t2 + lambda1*ml01_01_t2 + ml01_02_t2 + ml01_03_t2 + ml01_04_t2 + ml01_05_t2 + ml01_06_t2 + ml01_07_t2 + ml01_08_t2 + ml01_09_t2 + ml01_10_t2

# Intercepts
ml01_01_t1 ~ i1*1
ml01_02_t1 ~ 1
ml01_03_t1 ~ 1
ml01_04_t1 ~ 1
ml01_05_t1 ~ 1
ml01_06_t1 ~ 1
ml01_07_t1 ~ 1
ml01_08_t1 ~ 1
ml01_09_t1 ~ 1
ml01_10_t1 ~ 1

ml01_01_t2 ~ i1*1
ml01_02_t2 ~ 1
ml01_03_t2 ~ 1
ml01_04_t2 ~ 1
ml01_05_t2 ~ 1
ml01_06_t2 ~ 1
ml01_07_t2 ~ 1
ml01_08_t2 ~ 1
ml01_09_t2 ~ 1
ml01_10_t2 ~ 1

# Unique Variances
ml01_01_t1 ~~ ml01_01_t1
ml01_02_t1 ~~ ml01_02_t1
ml01_03_t1 ~~ ml01_03_t1
ml01_04_t1 ~~ ml01_04_t1
ml01_05_t1 ~~ ml01_05_t1
ml01_06_t1 ~~ ml01_06_t1
ml01_07_t1 ~~ ml01_07_t1
ml01_08_t1 ~~ ml01_08_t1
ml01_09_t1 ~~ ml01_09_t1
ml01_10_t1 ~~ ml01_10_t1

ml01_01_t2 ~~ ml01_01_t2
ml01_02_t2 ~~ ml01_02_t2
ml01_03_t2 ~~ ml01_03_t2
ml01_04_t2 ~~ ml01_04_t2
ml01_05_t2 ~~ ml01_05_t2
ml01_06_t2 ~~ ml01_06_t2
ml01_07_t2 ~~ ml01_07_t2
ml01_08_t2 ~~ ml01_08_t2
ml01_09_t2 ~~ ml01_09_t2
ml01_10_t2 ~~ ml01_10_t2

# Latent Variable Means
meaning1 ~ 0*1
meaning2 ~ 1

# Latent Variable Variances and Covariance
meaning1 ~~ 1*meaning1
meaning2 ~~ meaning2
meaning1 ~~ meaning2
'
fit_configural_meaning <- cfa(configural_meaning, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_configural_meaning, fit.measures = TRUE)

# Weak invariance model
weak_meaning <- '
# Define the latent factors
meaning1 =~ NA*ml01_01_t1 + lambda1*ml01_01_t1 + lambda2*ml01_02_t1 + lambda3*ml01_03_t1 + lambda4*ml01_04_t1 + lambda5*ml01_05_t1 + lambda6*ml01_06_t1 + lambda7*ml01_07_t1 + lambda8*ml01_08_t1 + lambda9*ml01_09_t1 + lambda10*ml01_10_t1 
meaning2 =~ NA*ml01_01_t2 + lambda1*ml01_01_t2 + lambda2*ml01_02_t2 + lambda3*ml01_03_t2 + lambda4*ml01_04_t2 + lambda5*ml01_05_t2 + lambda6*ml01_06_t2 + lambda7*ml01_07_t2 + lambda8*ml01_08_t2 + lambda9*ml01_09_t2 + lambda10*ml01_10_t2

# Intercepts
ml01_01_t1 ~ i1*1
ml01_02_t1 ~ 1
ml01_03_t1 ~ 1
ml01_04_t1 ~ 1
ml01_05_t1 ~ 1
ml01_06_t1 ~ 1
ml01_07_t1 ~ 1
ml01_08_t1 ~ 1
ml01_09_t1 ~ 1
ml01_10_t1 ~ 1

ml01_01_t2 ~ i1*1
ml01_02_t2 ~ 1
ml01_03_t2 ~ 1
ml01_04_t2 ~ 1
ml01_05_t2 ~ 1
ml01_06_t2 ~ 1
ml01_07_t2 ~ 1
ml01_08_t2 ~ 1
ml01_09_t2 ~ 1
ml01_10_t2 ~ 1

# Unique Variances
ml01_01_t1 ~~ ml01_01_t1
ml01_02_t1 ~~ ml01_02_t1
ml01_03_t1 ~~ ml01_03_t1
ml01_04_t1 ~~ ml01_04_t1
ml01_05_t1 ~~ ml01_05_t1
ml01_06_t1 ~~ ml01_06_t1
ml01_07_t1 ~~ ml01_07_t1
ml01_08_t1 ~~ ml01_08_t1
ml01_09_t1 ~~ ml01_09_t1
ml01_10_t1 ~~ ml01_10_t1

ml01_01_t2 ~~ ml01_01_t2
ml01_02_t2 ~~ ml01_02_t2
ml01_03_t2 ~~ ml01_03_t2
ml01_04_t2 ~~ ml01_04_t2
ml01_05_t2 ~~ ml01_05_t2
ml01_06_t2 ~~ ml01_06_t2
ml01_07_t2 ~~ ml01_07_t2
ml01_08_t2 ~~ ml01_08_t2
ml01_09_t2 ~~ ml01_09_t2
ml01_10_t2 ~~ ml01_10_t2

# Latent Variable Means
meaning1 ~ 0*1
meaning2 ~ 1

# Latent Variable Variances and Covariance
meaning1 ~~ 1*meaning1
meaning2 ~~ meaning2
meaning1 ~~ meaning2
'
fit_weak_meaning <- cfa(weak_meaning, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_weak_meaning, fit.measures = TRUE)

# Strong invariance model (additional constraints on manifest intercepts)
strong_meaning <- '
# Define the latent factors
meaning1 =~ NA*ml01_01_t1 + lambda1*ml01_01_t1 + lambda2*ml01_02_t1 + lambda3*ml01_03_t1 + lambda4*ml01_04_t1 + lambda5*ml01_05_t1 + lambda6*ml01_06_t1 + lambda7*ml01_07_t1 + lambda8*ml01_08_t1 + lambda9*ml01_09_t1 + lambda10*ml01_10_t1 
meaning2 =~ NA*ml01_01_t2 + lambda1*ml01_01_t2 + lambda2*ml01_02_t2 + lambda3*ml01_03_t2 + lambda4*ml01_04_t2 + lambda5*ml01_05_t2 + lambda6*ml01_06_t2 + lambda7*ml01_07_t2 + lambda8*ml01_08_t2 + lambda9*ml01_09_t2 + lambda10*ml01_10_t2

# Intercepts
ml01_01_t1 ~ i1*1
ml01_02_t1 ~ i2*1
ml01_03_t1 ~ i3*1
ml01_04_t1 ~ i4*1
ml01_05_t1 ~ i5*1
ml01_06_t1 ~ i6*1
ml01_07_t1 ~ i7*1
ml01_08_t1 ~ i8*1
ml01_09_t1 ~ i9*1
ml01_10_t1 ~ i10*1

ml01_01_t2 ~ i1*1
ml01_02_t2 ~ i2*1
ml01_03_t2 ~ i3*1
ml01_04_t2 ~ i4*1
ml01_05_t2 ~ i5*1
ml01_06_t2 ~ i6*1
ml01_07_t2 ~ i7*1
ml01_08_t2 ~ i8*1
ml01_09_t2 ~ i9*1
ml01_10_t2 ~ i10*1

# Unique Variances
ml01_01_t1 ~~ ml01_01_t1
ml01_02_t1 ~~ ml01_02_t1
ml01_03_t1 ~~ ml01_03_t1
ml01_04_t1 ~~ ml01_04_t1
ml01_05_t1 ~~ ml01_05_t1
ml01_06_t1 ~~ ml01_06_t1
ml01_07_t1 ~~ ml01_07_t1
ml01_08_t1 ~~ ml01_08_t1
ml01_09_t1 ~~ ml01_09_t1
ml01_10_t1 ~~ ml01_10_t1

ml01_01_t2 ~~ ml01_01_t2
ml01_02_t2 ~~ ml01_02_t2
ml01_03_t2 ~~ ml01_03_t2
ml01_04_t2 ~~ ml01_04_t2
ml01_05_t2 ~~ ml01_05_t2
ml01_06_t2 ~~ ml01_06_t2
ml01_07_t2 ~~ ml01_07_t2
ml01_08_t2 ~~ ml01_08_t2
ml01_09_t2 ~~ ml01_09_t2
ml01_10_t2 ~~ ml01_10_t2

# Latent Variable Means
meaning1 ~ 0*1
meaning2 ~ 1

# Latent Variable Variances and Covariance
meaning1 ~~ 1*meaning1
meaning2 ~~ meaning2
meaning1 ~~ meaning2
'
fit_strong_meaning <- cfa(strong_meaning, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_strong_meaning, fit.measures = TRUE)

# Strict invariance model (additional constraints on manifest variances)
strict_meaning <- '
# Define the latent factors
meaning1 =~ NA*ml01_01_t1 + lambda1*ml01_01_t1 + lambda2*ml01_02_t1 + lambda3*ml01_03_t1 + lambda4*ml01_04_t1 + lambda5*ml01_05_t1 + lambda6*ml01_06_t1 + lambda7*ml01_07_t1 + lambda8*ml01_08_t1 + lambda9*ml01_09_t1 + lambda10*ml01_10_t1 
meaning2 =~ NA*ml01_01_t2 + lambda1*ml01_01_t2 + lambda2*ml01_02_t2 + lambda3*ml01_03_t2 + lambda4*ml01_04_t2 + lambda5*ml01_05_t2 + lambda6*ml01_06_t2 + lambda7*ml01_07_t2 + lambda8*ml01_08_t2 + lambda9*ml01_09_t2 + lambda10*ml01_10_t2

# Intercepts
ml01_01_t1 ~ i1*1
ml01_02_t1 ~ i2*1
ml01_03_t1 ~ i3*1
ml01_04_t1 ~ i4*1
ml01_05_t1 ~ i5*1
ml01_06_t1 ~ i6*1
ml01_07_t1 ~ i7*1
ml01_08_t1 ~ i8*1
ml01_09_t1 ~ i9*1
ml01_10_t1 ~ i10*1

ml01_01_t2 ~ i1*1
ml01_02_t2 ~ i2*1
ml01_03_t2 ~ i3*1
ml01_04_t2 ~ i4*1
ml01_05_t2 ~ i5*1
ml01_06_t2 ~ i6*1
ml01_07_t2 ~ i7*1
ml01_08_t2 ~ i8*1
ml01_09_t2 ~ i9*1
ml01_10_t2 ~ i10*1

# Unique Variances
ml01_01_t1 ~~ u1*ml01_01_t1
ml01_02_t1 ~~ u2*ml01_02_t1
ml01_03_t1 ~~ u3*ml01_03_t1
ml01_04_t1 ~~ u4*ml01_04_t1
ml01_05_t1 ~~ u5*ml01_05_t1
ml01_06_t1 ~~ u6*ml01_06_t1
ml01_07_t1 ~~ u7*ml01_07_t1
ml01_08_t1 ~~ u8*ml01_08_t1
ml01_09_t1 ~~ u9*ml01_09_t1
ml01_10_t1 ~~ u10*ml01_10_t1

ml01_01_t2 ~~ u1*ml01_01_t2
ml01_02_t2 ~~ u2*ml01_02_t2
ml01_03_t2 ~~ u3*ml01_03_t2
ml01_04_t2 ~~ u4*ml01_04_t2
ml01_05_t2 ~~ u5*ml01_05_t2
ml01_06_t2 ~~ u6*ml01_06_t2
ml01_07_t2 ~~ u7*ml01_07_t2
ml01_08_t2 ~~ u8*ml01_08_t2
ml01_09_t2 ~~ u9*ml01_09_t2
ml01_10_t2 ~~ u10*ml01_10_t2

# Latent Variable Means
meaning1 ~ 0*1
meaning2 ~ 1

# Latent Variable Variances and Covariance
meaning1 ~~ 1*meaning1
meaning2 ~~ meaning2
meaning1 ~~ meaning2
'
fit_strict_meaning <- cfa(strict_meaning, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_strict_meaning, fit.measures = TRUE)
```

Results summary:
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5

# compare model fit
bind_rows(broom::glance(fit_configural_meaning) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_weak_meaning) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_strong_meaning) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_strict_meaning) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr)) %>% 
  mutate(model = c("configural", "weak", "strong", "strict")) %>% 
  select(model, everything())

# chi-square difference test for nested models 
anova(fit_configural_meaning, fit_weak_meaning)

anova(fit_weak_meaning, fit_strong_meaning)

anova(fit_strong_meaning, fit_strict_meaning)
```

::: {.callout-note appearance="minimal"}
Bad model fit across all model specifications. Chi^2 tests indicate that only weak measurement invariance is given.
:::

#### Self-esteem

Fit model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false
#| cache: true

# Code snippets adapted from https://quantdev.ssri.psu.edu/sites/qdev/files/LongitudinalMeasurementInvariance_2017_1108.html

# Configural invariance model
configural_selfes <- '
# Define the latent factors
selfes1 =~ NA*rs01_01_t1 + lambda1*rs01_01_t1 + rs01_02_t1 + rs01_03_t1 + rs01_04_t1 + rs01_05_t1 + rs01_06_t1 + rs01_07_t1 + rs01_08_t1 + rs01_09_t1 + rs01_10_t1
selfes2 =~ NA*rs01_01_t2 + lambda1*rs01_01_t2 + rs01_02_t2 + rs01_03_t2 + rs01_04_t2 + rs01_05_t2 + rs01_06_t2 + rs01_07_t2 + rs01_08_t2 + rs01_09_t2 + rs01_10_t2

# Intercepts
rs01_01_t1 ~ i1*1
rs01_02_t1 ~ 1
rs01_03_t1 ~ 1
rs01_04_t1 ~ 1
rs01_05_t1 ~ 1
rs01_06_t1 ~ 1
rs01_07_t1 ~ 1
rs01_08_t1 ~ 1
rs01_09_t1 ~ 1
rs01_10_t1 ~ 1

rs01_01_t2 ~ i1*1
rs01_02_t2 ~ 1
rs01_03_t2 ~ 1
rs01_04_t2 ~ 1
rs01_05_t2 ~ 1
rs01_06_t2 ~ 1
rs01_07_t2 ~ 1
rs01_08_t2 ~ 1
rs01_09_t2 ~ 1
rs01_10_t2 ~ 1

# Unique Variances
rs01_01_t1 ~~ rs01_01_t1
rs01_02_t1 ~~ rs01_02_t1
rs01_03_t1 ~~ rs01_03_t1
rs01_04_t1 ~~ rs01_04_t1
rs01_05_t1 ~~ rs01_05_t1
rs01_06_t1 ~~ rs01_06_t1
rs01_07_t1 ~~ rs01_07_t1
rs01_08_t1 ~~ rs01_08_t1
rs01_09_t1 ~~ rs01_09_t1
rs01_10_t1 ~~ rs01_10_t1

rs01_01_t2 ~~ rs01_01_t2
rs01_02_t2 ~~ rs01_02_t2
rs01_03_t2 ~~ rs01_03_t2
rs01_04_t2 ~~ rs01_04_t2
rs01_05_t2 ~~ rs01_05_t2
rs01_06_t2 ~~ rs01_06_t2
rs01_07_t2 ~~ rs01_07_t2
rs01_08_t2 ~~ rs01_08_t2
rs01_09_t2 ~~ rs01_09_t2
rs01_10_t2 ~~ rs01_10_t2

# Latent Variable Means
selfes1 ~ 0*1
selfes2 ~ 1

# Latent Variable Variances and Covariance
selfes1 ~~ 1*selfes1
selfes2 ~~ selfes2
selfes1 ~~ selfes2
'
fit_configural_selfes <- cfa(configural_selfes, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_configural_selfes, fit.measures = TRUE)

# Weak invariance model
weak_selfes <- '
# Define the latent factors
selfes1 =~ NA*rs01_01_t1 + lambda1*rs01_01_t1 + lambda2*rs01_02_t1 + lambda3*rs01_03_t1 + lambda4*rs01_04_t1 + lambda5*rs01_05_t1 + lambda6*rs01_06_t1 + lambda7*rs01_07_t1 + lambda8*rs01_08_t1 + lambda9*rs01_09_t1 + lambda10*rs01_10_t1 
selfes2 =~ NA*rs01_01_t2 + lambda1*rs01_01_t2 + lambda2*rs01_02_t2 + lambda3*rs01_03_t2 + lambda4*rs01_04_t2 + lambda5*rs01_05_t2 + lambda6*rs01_06_t2 + lambda7*rs01_07_t2 + lambda8*rs01_08_t2 + lambda9*rs01_09_t2 + lambda10*rs01_10_t2

# Intercepts
rs01_01_t1 ~ i1*1
rs01_02_t1 ~ 1
rs01_03_t1 ~ 1
rs01_04_t1 ~ 1
rs01_05_t1 ~ 1
rs01_06_t1 ~ 1
rs01_07_t1 ~ 1
rs01_08_t1 ~ 1
rs01_09_t1 ~ 1
rs01_10_t1 ~ 1

rs01_01_t2 ~ i1*1
rs01_02_t2 ~ 1
rs01_03_t2 ~ 1
rs01_04_t2 ~ 1
rs01_05_t2 ~ 1
rs01_06_t2 ~ 1
rs01_07_t2 ~ 1
rs01_08_t2 ~ 1
rs01_09_t2 ~ 1
rs01_10_t2 ~ 1

# Unique Variances
rs01_01_t1 ~~ rs01_01_t1
rs01_02_t1 ~~ rs01_02_t1
rs01_03_t1 ~~ rs01_03_t1
rs01_04_t1 ~~ rs01_04_t1
rs01_05_t1 ~~ rs01_05_t1
rs01_06_t1 ~~ rs01_06_t1
rs01_07_t1 ~~ rs01_07_t1
rs01_08_t1 ~~ rs01_08_t1
rs01_09_t1 ~~ rs01_09_t1
rs01_10_t1 ~~ rs01_10_t1

rs01_01_t2 ~~ rs01_01_t2
rs01_02_t2 ~~ rs01_02_t2
rs01_03_t2 ~~ rs01_03_t2
rs01_04_t2 ~~ rs01_04_t2
rs01_05_t2 ~~ rs01_05_t2
rs01_06_t2 ~~ rs01_06_t2
rs01_07_t2 ~~ rs01_07_t2
rs01_08_t2 ~~ rs01_08_t2
rs01_09_t2 ~~ rs01_09_t2
rs01_10_t2 ~~ rs01_10_t2

# Latent Variable Means
selfes1 ~ 0*1
selfes2 ~ 1

# Latent Variable Variances and Covariance
selfes1 ~~ 1*selfes1
selfes2 ~~ selfes2
selfes1 ~~ selfes2
'
fit_weak_selfes <- cfa(weak_selfes, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_weak_selfes, fit.measures = TRUE)

# Strong invariance model (additional constraints on manifest intercepts)
strong_selfes <- '
# Define the latent factors
selfes1 =~ NA*rs01_01_t1 + lambda1*rs01_01_t1 + lambda2*rs01_02_t1 + lambda3*rs01_03_t1 + lambda4*rs01_04_t1 + lambda5*rs01_05_t1 + lambda6*rs01_06_t1 + lambda7*rs01_07_t1 + lambda8*rs01_08_t1 + lambda9*rs01_09_t1 + lambda10*rs01_10_t1 
selfes2 =~ NA*rs01_01_t2 + lambda1*rs01_01_t2 + lambda2*rs01_02_t2 + lambda3*rs01_03_t2 + lambda4*rs01_04_t2 + lambda5*rs01_05_t2 + lambda6*rs01_06_t2 + lambda7*rs01_07_t2 + lambda8*rs01_08_t2 + lambda9*rs01_09_t2 + lambda10*rs01_10_t2

# Intercepts
rs01_01_t1 ~ i1*1
rs01_02_t1 ~ i2*1
rs01_03_t1 ~ i3*1
rs01_04_t1 ~ i4*1
rs01_05_t1 ~ i5*1
rs01_06_t1 ~ i6*1
rs01_07_t1 ~ i7*1
rs01_08_t1 ~ i8*1
rs01_09_t1 ~ i9*1
rs01_10_t1 ~ i10*1

rs01_01_t2 ~ i1*1
rs01_02_t2 ~ i2*1
rs01_03_t2 ~ i3*1
rs01_04_t2 ~ i4*1
rs01_05_t2 ~ i5*1
rs01_06_t2 ~ i6*1
rs01_07_t2 ~ i7*1
rs01_08_t2 ~ i8*1
rs01_09_t2 ~ i9*1
rs01_10_t2 ~ i10*1

# Unique Variances
rs01_01_t1 ~~ rs01_01_t1
rs01_02_t1 ~~ rs01_02_t1
rs01_03_t1 ~~ rs01_03_t1
rs01_04_t1 ~~ rs01_04_t1
rs01_05_t1 ~~ rs01_05_t1
rs01_06_t1 ~~ rs01_06_t1
rs01_07_t1 ~~ rs01_07_t1
rs01_08_t1 ~~ rs01_08_t1
rs01_09_t1 ~~ rs01_09_t1
rs01_10_t1 ~~ rs01_10_t1

rs01_01_t2 ~~ rs01_01_t2
rs01_02_t2 ~~ rs01_02_t2
rs01_03_t2 ~~ rs01_03_t2
rs01_04_t2 ~~ rs01_04_t2
rs01_05_t2 ~~ rs01_05_t2
rs01_06_t2 ~~ rs01_06_t2
rs01_07_t2 ~~ rs01_07_t2
rs01_08_t2 ~~ rs01_08_t2
rs01_09_t2 ~~ rs01_09_t2
rs01_10_t2 ~~ rs01_10_t2

# Latent Variable Means
selfes1 ~ 0*1
selfes2 ~ 1

# Latent Variable Variances and Covariance
selfes1 ~~ 1*selfes1
selfes2 ~~ selfes2
selfes1 ~~ selfes2
'
fit_strong_selfes <- cfa(strong_selfes, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_strong_selfes, fit.measures = TRUE)

# Strict invariance model (additional constraints on manifest variances)
strict_selfes <- '
# Define the latent factors
selfes1 =~ NA*rs01_01_t1 + lambda1*rs01_01_t1 + lambda2*rs01_02_t1 + lambda3*rs01_03_t1 + lambda4*rs01_04_t1 + lambda5*rs01_05_t1 + lambda6*rs01_06_t1 + lambda7*rs01_07_t1 + lambda8*rs01_08_t1 + lambda9*rs01_09_t1 + lambda10*rs01_10_t1 
selfes2 =~ NA*rs01_01_t2 + lambda1*rs01_01_t2 + lambda2*rs01_02_t2 + lambda3*rs01_03_t2 + lambda4*rs01_04_t2 + lambda5*rs01_05_t2 + lambda6*rs01_06_t2 + lambda7*rs01_07_t2 + lambda8*rs01_08_t2 + lambda9*rs01_09_t2 + lambda10*rs01_10_t2

# Intercepts
rs01_01_t1 ~ i1*1
rs01_02_t1 ~ i2*1
rs01_03_t1 ~ i3*1
rs01_04_t1 ~ i4*1
rs01_05_t1 ~ i5*1
rs01_06_t1 ~ i6*1
rs01_07_t1 ~ i7*1
rs01_08_t1 ~ i8*1
rs01_09_t1 ~ i9*1
rs01_10_t1 ~ i10*1

rs01_01_t2 ~ i1*1
rs01_02_t2 ~ i2*1
rs01_03_t2 ~ i3*1
rs01_04_t2 ~ i4*1
rs01_05_t2 ~ i5*1
rs01_06_t2 ~ i6*1
rs01_07_t2 ~ i7*1
rs01_08_t2 ~ i8*1
rs01_09_t2 ~ i9*1
rs01_10_t2 ~ i10*1

# Unique Variances
rs01_01_t1 ~~ u1*rs01_01_t1
rs01_02_t1 ~~ u2*rs01_02_t1
rs01_03_t1 ~~ u3*rs01_03_t1
rs01_04_t1 ~~ u4*rs01_04_t1
rs01_05_t1 ~~ u5*rs01_05_t1
rs01_06_t1 ~~ u6*rs01_06_t1
rs01_07_t1 ~~ u7*rs01_07_t1
rs01_08_t1 ~~ u8*rs01_08_t1
rs01_09_t1 ~~ u9*rs01_09_t1
rs01_10_t1 ~~ u10*rs01_10_t1

rs01_01_t2 ~~ u1*rs01_01_t2
rs01_02_t2 ~~ u2*rs01_02_t2
rs01_03_t2 ~~ u3*rs01_03_t2
rs01_04_t2 ~~ u4*rs01_04_t2
rs01_05_t2 ~~ u5*rs01_05_t2
rs01_06_t2 ~~ u6*rs01_06_t2
rs01_07_t2 ~~ u7*rs01_07_t2
rs01_08_t2 ~~ u8*rs01_08_t2
rs01_09_t2 ~~ u9*rs01_09_t2
rs01_10_t2 ~~ u10*rs01_10_t2

# Latent Variable Means
selfes1 ~ 0*1
selfes2 ~ 1

# Latent Variable Variances and Covariance
selfes1 ~~ 1*selfes1
selfes2 ~~ selfes2
selfes1 ~~ selfes2
'
fit_strict_selfes <- cfa(strict_selfes, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_strict_selfes, fit.measures = TRUE)
```

Results summary:
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5

# compare model fit
bind_rows(broom::glance(fit_configural_selfes) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_weak_selfes) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_strong_selfes) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_strict_selfes) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr)) %>% 
  mutate(model = c("configural", "weak", "strong", "strict")) %>% 
  select(model, everything())

# chi-square difference test for nested models 
anova(fit_configural_selfes, fit_weak_selfes)

anova(fit_weak_selfes, fit_strong_selfes)

anova(fit_strong_selfes, fit_strict_selfes)
```

::: {.callout-note appearance="minimal"}
Model fit relatively bad across all model specifications. Chi^2 tests indicate that strong measurement invariance is given.
:::

#### Self concept clarity

Fit model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false
#| cache: true

# Code snippets adapted from https://quantdev.ssri.psu.edu/sites/qdev/files/LongitudinalMeasurementInvariance_2017_1108.html

# Configural invariance model
configural_concept <- '
# Define the latent factors
concept1 =~ NA*sc01_01_t1 + lambda1*sc01_01_t1 + sc01_02_t1 + sc01_03_t1 + sc01_04_t1 + sc01_05_t1 + sc01_06_t1 + sc01_07_t1 + sc01_08_t1 + sc01_09_t1 + sc01_10_t1 + sc01_11_t1 + sc01_12_t1
concept2 =~ NA*sc01_01_t2 + lambda1*sc01_01_t2 + sc01_02_t2 + sc01_03_t2 + sc01_04_t2 + sc01_05_t2 + sc01_06_t2 + sc01_07_t2 + sc01_08_t2 + sc01_09_t2 + sc01_10_t2 + sc01_11_t2 + sc01_12_t2

# Intercepts
sc01_01_t1 ~ i1*1
sc01_02_t1 ~ 1
sc01_03_t1 ~ 1
sc01_04_t1 ~ 1
sc01_05_t1 ~ 1
sc01_06_t1 ~ 1
sc01_07_t1 ~ 1
sc01_08_t1 ~ 1
sc01_09_t1 ~ 1
sc01_10_t1 ~ 1
sc01_11_t1 ~ 1
sc01_12_t1 ~ 1

sc01_01_t2 ~ i1*1
sc01_02_t2 ~ 1
sc01_03_t2 ~ 1
sc01_04_t2 ~ 1
sc01_05_t2 ~ 1
sc01_06_t2 ~ 1
sc01_07_t2 ~ 1
sc01_08_t2 ~ 1
sc01_09_t2 ~ 1
sc01_10_t2 ~ 1
sc01_11_t2 ~ 1
sc01_12_t2 ~ 1

# Unique Variances
sc01_01_t1 ~~ sc01_01_t1
sc01_02_t1 ~~ sc01_02_t1
sc01_03_t1 ~~ sc01_03_t1
sc01_04_t1 ~~ sc01_04_t1
sc01_05_t1 ~~ sc01_05_t1
sc01_06_t1 ~~ sc01_06_t1
sc01_07_t1 ~~ sc01_07_t1
sc01_08_t1 ~~ sc01_08_t1
sc01_09_t1 ~~ sc01_09_t1
sc01_10_t1 ~~ sc01_10_t1
sc01_11_t1 ~~ sc01_11_t1
sc01_12_t1 ~~ sc01_12_t1

sc01_01_t2 ~~ sc01_01_t2
sc01_02_t2 ~~ sc01_02_t2
sc01_03_t2 ~~ sc01_03_t2
sc01_04_t2 ~~ sc01_04_t2
sc01_05_t2 ~~ sc01_05_t2
sc01_06_t2 ~~ sc01_06_t2
sc01_07_t2 ~~ sc01_07_t2
sc01_08_t2 ~~ sc01_08_t2
sc01_09_t2 ~~ sc01_09_t2
sc01_10_t2 ~~ sc01_10_t2
sc01_11_t2 ~~ sc01_11_t2
sc01_12_t2 ~~ sc01_12_t2

# Latent Variable Means
concept1 ~ 0*1
concept2 ~ 1

# Latent Variable Variances and Covariance
concept1 ~~ 1*concept1
concept2 ~~ concept2
concept1 ~~ concept2
'
fit_configural_concept <- cfa(configural_concept, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_configural_concept, fit.measures = TRUE)

# Weak invariance model
weak_concept <- '
# Define the latent factors
concept1 =~ NA*sc01_01_t1 + lambda1*sc01_01_t1 + lambda2*sc01_02_t1 + lambda3*sc01_03_t1 + lambda4*sc01_04_t1 + lambda5*sc01_05_t1 + lambda6*sc01_06_t1 + lambda7*sc01_07_t1 + lambda8*sc01_08_t1 + lambda9*sc01_09_t1 + lambda10*sc01_10_t1 + lambda11*sc01_11_t1 + lambda12*sc01_12_t1
concept2 =~ NA*sc01_01_t2 + lambda1*sc01_01_t2 + lambda2*sc01_02_t2 + lambda3*sc01_03_t2 + lambda4*sc01_04_t2 + lambda5*sc01_05_t2 + lambda6*sc01_06_t2 + lambda7*sc01_07_t2 + lambda8*sc01_08_t2 + lambda9*sc01_09_t2 + lambda10*sc01_10_t2 + lambda11*sc01_11_t2 + lambda12*sc01_12_t2

# Intercepts
sc01_01_t1 ~ i1*1
sc01_02_t1 ~ 1
sc01_03_t1 ~ 1
sc01_04_t1 ~ 1
sc01_05_t1 ~ 1
sc01_06_t1 ~ 1
sc01_07_t1 ~ 1
sc01_08_t1 ~ 1
sc01_09_t1 ~ 1
sc01_10_t1 ~ 1
sc01_11_t1 ~ 1
sc01_12_t1 ~ 1

sc01_01_t2 ~ i1*1
sc01_02_t2 ~ 1
sc01_03_t2 ~ 1
sc01_04_t2 ~ 1
sc01_05_t2 ~ 1
sc01_06_t2 ~ 1
sc01_07_t2 ~ 1
sc01_08_t2 ~ 1
sc01_09_t2 ~ 1
sc01_10_t2 ~ 1
sc01_11_t2 ~ 1
sc01_12_t2 ~ 1

# Unique Variances
sc01_01_t1 ~~ sc01_01_t1
sc01_02_t1 ~~ sc01_02_t1
sc01_03_t1 ~~ sc01_03_t1
sc01_04_t1 ~~ sc01_04_t1
sc01_05_t1 ~~ sc01_05_t1
sc01_06_t1 ~~ sc01_06_t1
sc01_07_t1 ~~ sc01_07_t1
sc01_08_t1 ~~ sc01_08_t1
sc01_09_t1 ~~ sc01_09_t1
sc01_10_t1 ~~ sc01_10_t1
sc01_11_t1 ~~ sc01_11_t1
sc01_12_t1 ~~ sc01_12_t1

sc01_01_t2 ~~ sc01_01_t2
sc01_02_t2 ~~ sc01_02_t2
sc01_03_t2 ~~ sc01_03_t2
sc01_04_t2 ~~ sc01_04_t2
sc01_05_t2 ~~ sc01_05_t2
sc01_06_t2 ~~ sc01_06_t2
sc01_07_t2 ~~ sc01_07_t2
sc01_08_t2 ~~ sc01_08_t2
sc01_09_t2 ~~ sc01_09_t2
sc01_10_t2 ~~ sc01_10_t2
sc01_11_t2 ~~ sc01_11_t2
sc01_12_t2 ~~ sc01_12_t2

# Latent Variable Means
concept1 ~ 0*1
concept2 ~ 1

# Latent Variable Variances and Covariance
concept1 ~~ 1*concept1
concept2 ~~ concept2
concept1 ~~ concept2
'
fit_weak_concept <- cfa(weak_concept, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_weak_concept, fit.measures = TRUE)

# Strong invariance model (additional constraints on manifest intercepts)
strong_concept <- '
# Define the latent factors
concept1 =~ NA*sc01_01_t1 + lambda1*sc01_01_t1 + lambda2*sc01_02_t1 + lambda3*sc01_03_t1 + lambda4*sc01_04_t1 + lambda5*sc01_05_t1 + lambda6*sc01_06_t1 + lambda7*sc01_07_t1 + lambda8*sc01_08_t1 + lambda9*sc01_09_t1 + lambda10*sc01_10_t1 + lambda11*sc01_11_t1 + lambda12*sc01_12_t1
concept2 =~ NA*sc01_01_t2 + lambda1*sc01_01_t2 + lambda2*sc01_02_t2 + lambda3*sc01_03_t2 + lambda4*sc01_04_t2 + lambda5*sc01_05_t2 + lambda6*sc01_06_t2 + lambda7*sc01_07_t2 + lambda8*sc01_08_t2 + lambda9*sc01_09_t2 + lambda10*sc01_10_t2 + lambda11*sc01_11_t2 + lambda12*sc01_12_t2

# Intercepts
sc01_01_t1 ~ i1*1
sc01_02_t1 ~ i2*1
sc01_03_t1 ~ i3*1
sc01_04_t1 ~ i4*1
sc01_05_t1 ~ i5*1
sc01_06_t1 ~ i6*1
sc01_07_t1 ~ i7*1
sc01_08_t1 ~ i8*1
sc01_09_t1 ~ i9*1
sc01_10_t1 ~ i10*1
sc01_11_t1 ~ i11*1
sc01_12_t1 ~ i12*1

sc01_01_t2 ~ i1*1
sc01_02_t2 ~ i2*1
sc01_03_t2 ~ i3*1
sc01_04_t2 ~ i4*1
sc01_05_t2 ~ i5*1
sc01_06_t2 ~ i6*1
sc01_07_t2 ~ i7*1
sc01_08_t2 ~ i8*1
sc01_09_t2 ~ i9*1
sc01_10_t2 ~ i10*1
sc01_11_t2 ~ i11*1
sc01_12_t2 ~ i12*1

# Unique Variances
sc01_01_t1 ~~ sc01_01_t1
sc01_02_t1 ~~ sc01_02_t1
sc01_03_t1 ~~ sc01_03_t1
sc01_04_t1 ~~ sc01_04_t1
sc01_05_t1 ~~ sc01_05_t1
sc01_06_t1 ~~ sc01_06_t1
sc01_07_t1 ~~ sc01_07_t1
sc01_08_t1 ~~ sc01_08_t1
sc01_09_t1 ~~ sc01_09_t1
sc01_10_t1 ~~ sc01_10_t1
sc01_11_t1 ~~ sc01_11_t1
sc01_12_t1 ~~ sc01_12_t1

sc01_01_t2 ~~ sc01_01_t2
sc01_02_t2 ~~ sc01_02_t2
sc01_03_t2 ~~ sc01_03_t2
sc01_04_t2 ~~ sc01_04_t2
sc01_05_t2 ~~ sc01_05_t2
sc01_06_t2 ~~ sc01_06_t2
sc01_07_t2 ~~ sc01_07_t2
sc01_08_t2 ~~ sc01_08_t2
sc01_09_t2 ~~ sc01_09_t2
sc01_10_t2 ~~ sc01_10_t2
sc01_11_t2 ~~ sc01_11_t2
sc01_12_t2 ~~ sc01_12_t2

# Latent Variable Means
concept1 ~ 0*1
concept2 ~ 1

# Latent Variable Variances and Covariance
concept1 ~~ 1*concept1
concept2 ~~ concept2
concept1 ~~ concept2
'
fit_strong_concept <- cfa(strong_concept, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_strong_concept, fit.measures = TRUE)

# Strict invariance model (additional constraints on manifest variances)
strict_concept <- '
# Define the latent factors
concept1 =~ NA*sc01_01_t1 + lambda1*sc01_01_t1 + lambda2*sc01_02_t1 + lambda3*sc01_03_t1 + lambda4*sc01_04_t1 + lambda5*sc01_05_t1 + lambda6*sc01_06_t1 + lambda7*sc01_07_t1 + lambda8*sc01_08_t1 + lambda9*sc01_09_t1 + lambda10*sc01_10_t1 + lambda11*sc01_11_t1 + lambda12*sc01_12_t1
concept2 =~ NA*sc01_01_t2 + lambda1*sc01_01_t2 + lambda2*sc01_02_t2 + lambda3*sc01_03_t2 + lambda4*sc01_04_t2 + lambda5*sc01_05_t2 + lambda6*sc01_06_t2 + lambda7*sc01_07_t2 + lambda8*sc01_08_t2 + lambda9*sc01_09_t2 + lambda10*sc01_10_t2 + lambda11*sc01_11_t2 + lambda12*sc01_12_t2

# Intercepts
sc01_01_t1 ~ i1*1
sc01_02_t1 ~ i2*1
sc01_03_t1 ~ i3*1
sc01_04_t1 ~ i4*1
sc01_05_t1 ~ i5*1
sc01_06_t1 ~ i6*1
sc01_07_t1 ~ i7*1
sc01_08_t1 ~ i8*1
sc01_09_t1 ~ i9*1
sc01_10_t1 ~ i10*1
sc01_11_t1 ~ i11*1
sc01_12_t1 ~ i12*1

sc01_01_t2 ~ i1*1
sc01_02_t2 ~ i2*1
sc01_03_t2 ~ i3*1
sc01_04_t2 ~ i4*1
sc01_05_t2 ~ i5*1
sc01_06_t2 ~ i6*1
sc01_07_t2 ~ i7*1
sc01_08_t2 ~ i8*1
sc01_09_t2 ~ i9*1
sc01_10_t2 ~ i10*1
sc01_11_t2 ~ i11*1
sc01_12_t2 ~ i12*1

# Unique Variances
sc01_01_t1 ~~ u1*sc01_01_t1
sc01_02_t1 ~~ u2*sc01_02_t1
sc01_03_t1 ~~ u3*sc01_03_t1
sc01_04_t1 ~~ u4*sc01_04_t1
sc01_05_t1 ~~ u5*sc01_05_t1
sc01_06_t1 ~~ u6*sc01_06_t1
sc01_07_t1 ~~ u7*sc01_07_t1
sc01_08_t1 ~~ u8*sc01_08_t1
sc01_09_t1 ~~ u9*sc01_09_t1
sc01_10_t1 ~~ u10*sc01_10_t1
sc01_11_t1 ~~ u11*sc01_11_t1
sc01_12_t1 ~~ u12*sc01_12_t1

sc01_01_t2 ~~ u1*sc01_01_t2
sc01_02_t2 ~~ u2*sc01_02_t2
sc01_03_t2 ~~ u3*sc01_03_t2
sc01_04_t2 ~~ u4*sc01_04_t2
sc01_05_t2 ~~ u5*sc01_05_t2
sc01_06_t2 ~~ u6*sc01_06_t2
sc01_07_t2 ~~ u7*sc01_07_t2
sc01_08_t2 ~~ u8*sc01_08_t2
sc01_09_t2 ~~ u9*sc01_09_t2
sc01_10_t2 ~~ u10*sc01_10_t2
sc01_11_t2 ~~ u11*sc01_11_t2
sc01_12_t2 ~~ u12*sc01_12_t2

# Latent Variable Means
concept1 ~ 0*1
concept2 ~ 1

# Latent Variable Variances and Covariance
concept1 ~~ 1*concept1
concept2 ~~ concept2
concept1 ~~ concept2
'
fit_strict_concept <- cfa(strict_concept, data = df_sbsa_wide_wb, mimic = "mplus")
summary(fit_strict_concept, fit.measures = TRUE)
```

Results summary:
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5

# compare model fit
bind_rows(broom::glance(fit_configural_concept) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_weak_concept) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_strong_concept) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr),
          broom::glance(fit_strict_concept) %>% 
            select(nobs, npar, chisq, AIC, BIC, cfi, tli, rmsea, srmr)) %>% 
  mutate(model = c("configural", "weak", "strong", "strict")) %>% 
  select(model, everything())

# chi-square difference test for nested models 
anova(fit_configural_concept, fit_weak_concept)

anova(fit_weak_concept, fit_strong_concept)

anova(fit_strong_concept, fit_strict_concept)
```

::: {.callout-note appearance="minimal"}
Relatively bad model fit across all model specifications. Chi^2 tests indicate that only weak measurement invariance is given.
:::

------------------------------------------------------------------------

### Hypothesis 2: Well-being - latent change {#hyp2}

*Both groups will increase in all four psychological well-being indicators.* 

We will test the mean-level difference between baseline and follow up using a latent change model.

#### Life satisfaction

Fit model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false
#| cache: true

# Code snippets adapted from Kievit et al. (2018) -- CC-BY -- https://doi.org/10.1016/j.dcn.2017.11.007

# Fit the multiple indicator Univariate Latent Change Score model
mi_lcs_swls_hyp2 <- '
swls_t1 =~ 1*sw06_01_t1 + lamb2*sw06_02_t1 + lamb3*sw06_03_t1 + lamb4*sw06_04_t1 + lamb5*sw06_05_t1 # This specifies the measurement model for swls_t1 
swls_t2 =~ 1*sw06_01_t2 + lamb2*sw06_02_t2 + lamb3*sw06_03_t2 + lamb4*sw06_04_t2 + lamb5*sw06_05_t2 # This specifies the measurement model for swls_t2 with the equality constrained factor loadings

swls_t2 ~ 1*swls_t1     # This parameter regresses swls_t2 perfectly on swls_t1
d_swls_1 =~ 1*swls_t2   # This defines the latent change score factor as measured perfectly by scores on swls_t2
swls_t2 ~ 0*1           # This line constrains the intercept of swls_t2 to 0
swls_t2 ~~ 0*swls_t2    # This fixes the variance of swls_t2 to 0

d_swls_1 ~ 1           # This estimates the intercept of the change score 
swls_t1 ~ 1            # This estimates the intercept of swls_t1 
d_swls_1 ~~ d_swls_1   # This estimates the variance of the change scores 
swls_t1 ~~ swls_t1     # This estimates the variance of the swls_t1 
d_swls_1 ~ swls_t1     # This estimates the self-feedback parameter

sw06_01_t1 ~~ sw06_01_t2   # This allows residual covariance on indicator X1 across T1 and T2
sw06_02_t1 ~~ sw06_02_t2   # This allows residual covariance on indicator X2 across T1 and T2
sw06_03_t1 ~~ sw06_03_t2   # This allows residual covariance on indicator X3 across T1 and T2
sw06_04_t1 ~~ sw06_04_t2   # This allows residual covariance on indicator X4 across T1 and T2
sw06_05_t1 ~~ sw06_05_t2   # This allows residual covariance on indicator X5 across T1 and T2

sw06_01_t1 ~~ res1*sw06_01_t1   # This allows residual variance on indicator X1 at T1 
sw06_02_t1 ~~ res2*sw06_02_t1   # This allows residual variance on indicator X2 at T1
sw06_03_t1 ~~ res3*sw06_03_t1   # This allows residual variance on indicator X3 at T1
sw06_04_t1 ~~ res4*sw06_04_t1   # This allows residual variance on indicator X4 at T1
sw06_05_t1 ~~ res5*sw06_05_t1   # This allows residual variance on indicator X5 at T1

sw06_01_t2 ~~ res1*sw06_01_t2  # This allows residual variance on indicator X1 at T2 
sw06_02_t2 ~~ res2*sw06_02_t2  # This allows residual variance on indicator X2 at T2 
sw06_03_t2 ~~ res3*sw06_03_t2  # This allows residual variance on indicator X3 at T2
sw06_04_t2 ~~ res4*sw06_04_t2  # This allows residual variance on indicator X4 at T2
sw06_05_t2 ~~ res5*sw06_05_t2  # This allows residual variance on indicator X5 at T2

sw06_01_t1 ~ 0*1      # This constrains the intercept of X1 to 0 at T1
sw06_02_t1 ~ m2*1     # This estimates the intercept of X2 at T1
sw06_03_t1 ~ m3*1     # This estimates the intercept of X3 at T1
sw06_04_t1 ~ m4*1     # This estimates the intercept of X4 at T1
sw06_05_t1 ~ m5*1     # This estimates the intercept of X5 at T1

sw06_01_t2 ~ 0*1      # This constrains the intercept of X1 to 0 at T2
sw06_02_t2 ~ m2*1     # This estimates the intercept of X2 at T2
sw06_03_t2 ~ m3*1     # This estimates the intercept of X3 at T2
sw06_04_t2 ~ m4*1     # This estimates the intercept of X4 at T2
sw06_05_t2 ~ m5*1     # This estimates the intercept of X5 at T2
'
fit_mi_lcs_swls_hyp2 <- lavaan(mi_lcs_swls_hyp2, data=df_sbsa_wide_wb, estimator='mlr', fixed.x=FALSE, missing='fiml')
summary(fit_mi_lcs_swls_hyp2, fit.measures=TRUE, standardized=TRUE, rsquare=F)
```

Results summary:
```{r}
#| echo: true

# model fit
kable(broom::glance(fit_mi_lcs_swls_hyp2) %>% 
        select(nobs, npar, AIC, BIC, cfi, rmsea, srmr), digits = 3)

# parameters of interest
kable(broom::tidy(fit_mi_lcs_swls_hyp2, conf.int = FALSE, conf.level = 0.95) %>% 
        select(term, estimate, std.all, statistic, p.value) %>% 
        filter(term %in% c("swls_t2 ~ swls_t1", "d_swls_1 =~ swls_t2", "d_swls_1 ~ swls_t1", # change parameters
                           "d_swls_1 ~1 ", "swls_t1 ~1 ", "", # means
                           "d_swls_1 ~~ d_swls_1")), digits = 3) # variances
```

Plot model:
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5

semPaths(fit_mi_lcs_swls_hyp2, what="est", 
         sizeLat = 7, sizeMan = 7, edge.label.cex = .75, intercepts = T, edge.color="black")
```

::: {.callout-note appearance="minimal"}
Significantly higher life satisfaction at the post test. Those with initially higher levels of life satisfaction (at T1) change to a lesser degree.
:::

#### Meaning in life

Fit model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false
#| cache: true

# Code snippets adapted from Kievit et al. (2018) -- CC-BY -- https://doi.org/10.1016/j.dcn.2017.11.007

# Fit the multiple indicator Univariate Latent Change Score model
mi_lcs_meaning_hyp2 <- '
meaning_t1 =~ 1*ml01_01_t1 + lamb2*ml01_02_t1 + lamb3*ml01_03_t1 + lamb4*ml01_04_t1 + lamb5*ml01_05_t1 + lamb6*ml01_06_t1 + lamb7*ml01_07_t1 + lamb8*ml01_08_t1 + lamb9*ml01_09_t1 + lamb10*ml01_10_t1 # This specifies the measurement model for meaning_t1 
meaning_t2 =~ 1*ml01_01_t2 + lamb2*ml01_02_t2 + lamb3*ml01_03_t2 + lamb4*ml01_04_t2 + lamb5*ml01_05_t2 + lamb6*ml01_06_t2 + lamb7*ml01_07_t2 + lamb8*ml01_08_t2 + lamb9*ml01_09_t2 + lamb10*ml01_10_t2 # This specifies the measurement model for meaning_t2 with the equality constrained factor loadings

meaning_t2 ~ 1*meaning_t1     # This parameter regresses meaning_t2 perfectly on meaning_t1
d_meaning_1 =~ 1*meaning_t2   # This defines the latent change score factor as measured perfectly by scores on meaning_t2
meaning_t2 ~ 0*1              # This line constrains the intercept of meaning_t2 to 0
meaning_t2 ~~ 0*meaning_t2    # This fixes the variance of meaning_t2 to 0

d_meaning_1 ~ 1              # This estimates the intercept of the change score 
meaning_t1 ~ 1               # This estimates the intercept of meaning_t1 
d_meaning_1 ~~ d_meaning_1   # This estimates the variance of the change scores 
meaning_t1 ~~ meaning_t1     # This estimates the variance of the meaning_t1 
d_meaning_1 ~ meaning_t1     # This estimates the self-feedback parameter

ml01_01_t1 ~~ ml01_01_t2   # This allows residual covariance on indicator X1 across T1 and T2
ml01_02_t1 ~~ ml01_02_t2   # This allows residual covariance on indicator X2 across T1 and T2
ml01_03_t1 ~~ ml01_03_t2   # This allows residual covariance on indicator X3 across T1 and T2
ml01_04_t1 ~~ ml01_04_t2   # This allows residual covariance on indicator X4 across T1 and T2
ml01_05_t1 ~~ ml01_05_t2   # This allows residual covariance on indicator X5 across T1 and T2
ml01_06_t1 ~~ ml01_06_t2   # This allows residual covariance on indicator X6 across T1 and T2
ml01_07_t1 ~~ ml01_07_t2   # This allows residual covariance on indicator X7 across T1 and T2
ml01_08_t1 ~~ ml01_08_t2   # This allows residual covariance on indicator X8 across T1 and T2
ml01_09_t1 ~~ ml01_09_t2   # This allows residual covariance on indicator X9 across T1 and T2
ml01_10_t1 ~~ ml01_10_t2   # This allows residual covariance on indicator X10 across T1 and T2

ml01_01_t1 ~~ res1*ml01_01_t1   # This allows residual variance on indicator X1 at T1 
ml01_02_t1 ~~ res2*ml01_02_t1   # This allows residual variance on indicator X2 at T1
ml01_03_t1 ~~ res3*ml01_03_t1   # This allows residual variance on indicator X3 at T1
ml01_04_t1 ~~ res4*ml01_04_t1   # This allows residual variance on indicator X4 at T1
ml01_05_t1 ~~ res5*ml01_05_t1   # This allows residual variance on indicator X5 at T1
ml01_06_t1 ~~ res6*ml01_06_t1   # This allows residual variance on indicator X6 at T1 
ml01_07_t1 ~~ res7*ml01_07_t1   # This allows residual variance on indicator X7 at T1
ml01_08_t1 ~~ res8*ml01_08_t1   # This allows residual variance on indicator X8 at T1
ml01_09_t1 ~~ res9*ml01_09_t1   # This allows residual variance on indicator X9 at T1
ml01_10_t1 ~~ res10*ml01_10_t1  # This allows residual variance on indicator X10 at T1

ml01_01_t2 ~~ res1*ml01_01_t2  # This allows residual variance on indicator X1 at T2 
ml01_02_t2 ~~ res2*ml01_02_t2  # This allows residual variance on indicator X2 at T2 
ml01_03_t2 ~~ res3*ml01_03_t2  # This allows residual variance on indicator X3 at T2
ml01_04_t2 ~~ res4*ml01_04_t2  # This allows residual variance on indicator X4 at T2
ml01_05_t2 ~~ res5*ml01_05_t2  # This allows residual variance on indicator X5 at T2
ml01_06_t2 ~~ res6*ml01_06_t2  # This allows residual variance on indicator X6 at T2 
ml01_07_t2 ~~ res7*ml01_07_t2  # This allows residual variance on indicator X7 at T2 
ml01_08_t2 ~~ res8*ml01_08_t2  # This allows residual variance on indicator X8 at T2
ml01_09_t2 ~~ res9*ml01_09_t2  # This allows residual variance on indicator X9 at T2
ml01_10_t2 ~~ res10*ml01_10_t2 # This allows residual variance on indicator X10 at T2

ml01_01_t1 ~ 0*1      # This constrains the intercept of X1 to 0 at T1
ml01_02_t1 ~ m2*1     # This estimates the intercept of X2 at T1
ml01_03_t1 ~ m3*1     # This estimates the intercept of X3 at T1
ml01_04_t1 ~ m4*1     # This estimates the intercept of X4 at T1
ml01_05_t1 ~ m5*1     # This estimates the intercept of X5 at T1
ml01_06_t1 ~ m6*1     # This estimates the intercept of X6 at T1
ml01_07_t1 ~ m7*1     # This estimates the intercept of X7 at T1
ml01_08_t1 ~ m8*1     # This estimates the intercept of X8 at T1
ml01_09_t1 ~ m9*1     # This estimates the intercept of X9 at T1
ml01_10_t1 ~ m10*1    # This estimates the intercept of X10 at T1

ml01_01_t2 ~ 0*1      # This constrains the intercept of X1 to 0 at T2
ml01_02_t2 ~ m2*1     # This estimates the intercept of X2 at T2
ml01_03_t2 ~ m3*1     # This estimates the intercept of X3 at T2
ml01_04_t2 ~ m4*1     # This estimates the intercept of X4 at T2
ml01_05_t2 ~ m5*1     # This estimates the intercept of X5 at T2
ml01_06_t2 ~ m6*1     # This estimates the intercept of X6 at T2
ml01_07_t2 ~ m7*1     # This estimates the intercept of X7 at T2
ml01_08_t2 ~ m8*1     # This estimates the intercept of X8 at T2
ml01_09_t2 ~ m9*1     # This estimates the intercept of X9 at T2
ml01_10_t2 ~ m10*1    # This estimates the intercept of X10 at T2
'
fit_mi_lcs_meaning_hyp2 <- lavaan(mi_lcs_meaning_hyp2, data=df_sbsa_wide_wb, estimator='mlr', fixed.x=FALSE, missing='fiml')
summary(fit_mi_lcs_meaning_hyp2, fit.measures=TRUE, standardized=TRUE, rsquare=F)
```

Results summary:
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5

# model fit
kable(broom::glance(fit_mi_lcs_meaning_hyp2) %>% 
        select(nobs, npar, AIC, BIC, cfi, rmsea, srmr), digits = 3)

# parameters of interest
kable(broom::tidy(fit_mi_lcs_meaning_hyp2, conf.int = FALSE, conf.level = 0.95) %>% 
        select(term, estimate, std.all, statistic, p.value) %>% 
        filter(term %in% c("meaning_t2 ~ meaning_t1", "d_meaning_1 =~ meaning_t2", "d_meaning_1 ~ meaning_t1", # change parameters
                           "d_meaning_1 ~1 ", "meaning_t1 ~1 ", "", # means
                           "d_meaning_1 ~~ d_meaning_1")), digits = 3) # variances
```

::: {.callout-note appearance="minimal"}
Very bad model fit... Participants improved significantly in meaning in life across time. 
:::

#### Self-esteem

Fit model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false
#| cache: true

# Code snippets adapted from Kievit et al. (2018) -- CC-BY -- https://doi.org/10.1016/j.dcn.2017.11.007

# Fit the multiple indicator Univariate Latent Change Score model
mi_lcs_selfes_hyp2 <- '
selfes_t1 =~ 1*rs01_01_t1 + lamb2*rs01_02_t1 + lamb3*rs01_03_t1 + lamb4*rs01_04_t1 + lamb5*rs01_05_t1 + lamb6*rs01_06_t1 + lamb7*rs01_07_t1 + lamb8*rs01_08_t1 + lamb9*rs01_09_t1 + lamb10*rs01_10_t1 # This specifies the measurement model for selfes_t1 
selfes_t2 =~ 1*rs01_01_t2 + lamb2*rs01_02_t2 + lamb3*rs01_03_t2 + lamb4*rs01_04_t2 + lamb5*rs01_05_t2 + lamb6*rs01_06_t2 + lamb7*rs01_07_t2 + lamb8*rs01_08_t2 + lamb9*rs01_09_t2 + lamb10*rs01_10_t2 # This specifies the measurement model for selfes_t2 with the equality constrained factor loadings

selfes_t2 ~ 1*selfes_t1     # This parameter regresses selfes_t2 perfectly on selfes_t1
d_selfes_1 =~ 1*selfes_t2   # This defines the latent change score factor as measured perfectly by scores on selfes_t2
selfes_t2 ~ 0*1             # This line constrains the intercept of selfes_t2 to 0
selfes_t2 ~~ 0*selfes_t2    # This fixes the variance of selfes_t2 to 0

d_selfes_1 ~ 1             # This estimates the intercept of the change score 
selfes_t1 ~ 1              # This estimates the intercept of selfes_t1 
d_selfes_1 ~~ d_selfes_1   # This estimates the variance of the change scores 
selfes_t1 ~~ selfes_t1     # This estimates the variance of the selfes_t1 
d_selfes_1 ~ selfes_t1     # This estimates the self-feedback parameter

rs01_01_t1 ~~ rs01_01_t2   # This allows residual covariance on indicator X1 across T1 and T2
rs01_02_t1 ~~ rs01_02_t2   # This allows residual covariance on indicator X2 across T1 and T2
rs01_03_t1 ~~ rs01_03_t2   # This allows residual covariance on indicator X3 across T1 and T2
rs01_04_t1 ~~ rs01_04_t2   # This allows residual covariance on indicator X4 across T1 and T2
rs01_05_t1 ~~ rs01_05_t2   # This allows residual covariance on indicator X5 across T1 and T2
rs01_06_t1 ~~ rs01_06_t2   # This allows residual covariance on indicator X6 across T1 and T2
rs01_07_t1 ~~ rs01_07_t2   # This allows residual covariance on indicator X7 across T1 and T2
rs01_08_t1 ~~ rs01_08_t2   # This allows residual covariance on indicator X8 across T1 and T2
rs01_09_t1 ~~ rs01_09_t2   # This allows residual covariance on indicator X9 across T1 and T2
rs01_10_t1 ~~ rs01_10_t2   # This allows residual covariance on indicator X10 across T1 and T2

rs01_01_t1 ~~ res1*rs01_01_t1   # This allows residual variance on indicator X1 at T1 
rs01_02_t1 ~~ res2*rs01_02_t1   # This allows residual variance on indicator X2 at T1
rs01_03_t1 ~~ res3*rs01_03_t1   # This allows residual variance on indicator X3 at T1
rs01_04_t1 ~~ res4*rs01_04_t1   # This allows residual variance on indicator X4 at T1
rs01_05_t1 ~~ res5*rs01_05_t1   # This allows residual variance on indicator X5 at T1
rs01_06_t1 ~~ res6*rs01_06_t1   # This allows residual variance on indicator X6 at T1 
rs01_07_t1 ~~ res7*rs01_07_t1   # This allows residual variance on indicator X7 at T1
rs01_08_t1 ~~ res8*rs01_08_t1   # This allows residual variance on indicator X8 at T1
rs01_09_t1 ~~ res9*rs01_09_t1   # This allows residual variance on indicator X9 at T1
rs01_10_t1 ~~ res10*rs01_10_t1  # This allows residual variance on indicator X10 at T1

rs01_01_t2 ~~ res1*rs01_01_t2  # This allows residual variance on indicator X1 at T2 
rs01_02_t2 ~~ res2*rs01_02_t2  # This allows residual variance on indicator X2 at T2 
rs01_03_t2 ~~ res3*rs01_03_t2  # This allows residual variance on indicator X3 at T2
rs01_04_t2 ~~ res4*rs01_04_t2  # This allows residual variance on indicator X4 at T2
rs01_05_t2 ~~ res5*rs01_05_t2  # This allows residual variance on indicator X5 at T2
rs01_06_t2 ~~ res6*rs01_06_t2  # This allows residual variance on indicator X6 at T2 
rs01_07_t2 ~~ res7*rs01_07_t2  # This allows residual variance on indicator X7 at T2 
rs01_08_t2 ~~ res8*rs01_08_t2  # This allows residual variance on indicator X8 at T2
rs01_09_t2 ~~ res9*rs01_09_t2  # This allows residual variance on indicator X9 at T2
rs01_10_t2 ~~ res10*rs01_10_t2 # This allows residual variance on indicator X10 at T2

rs01_01_t1 ~ 0*1      # This constrains the intercept of X1 to 0 at T1
rs01_02_t1 ~ m2*1     # This estimates the intercept of X2 at T1
rs01_03_t1 ~ m3*1     # This estimates the intercept of X3 at T1
rs01_04_t1 ~ m4*1     # This estimates the intercept of X4 at T1
rs01_05_t1 ~ m5*1     # This estimates the intercept of X5 at T1
rs01_06_t1 ~ m6*1     # This estimates the intercept of X6 at T1
rs01_07_t1 ~ m7*1     # This estimates the intercept of X7 at T1
rs01_08_t1 ~ m8*1     # This estimates the intercept of X8 at T1
rs01_09_t1 ~ m9*1     # This estimates the intercept of X9 at T1
rs01_10_t1 ~ m10*1    # This estimates the intercept of X10 at T1

rs01_01_t2 ~ 0*1      # This constrains the intercept of X1 to 0 at T2
rs01_02_t2 ~ m2*1     # This estimates the intercept of X2 at T2
rs01_03_t2 ~ m3*1     # This estimates the intercept of X3 at T2
rs01_04_t2 ~ m4*1     # This estimates the intercept of X4 at T2
rs01_05_t2 ~ m5*1     # This estimates the intercept of X5 at T2
rs01_06_t2 ~ m6*1     # This estimates the intercept of X6 at T2
rs01_07_t2 ~ m7*1     # This estimates the intercept of X7 at T2
rs01_08_t2 ~ m8*1     # This estimates the intercept of X8 at T2
rs01_09_t2 ~ m9*1     # This estimates the intercept of X9 at T2
rs01_10_t2 ~ m10*1    # This estimates the intercept of X10 at T2
'
fit_mi_lcs_selfes_hyp2 <- lavaan(mi_lcs_selfes_hyp2, data=df_sbsa_wide_wb, estimator='mlr', fixed.x=FALSE, missing='fiml')
summary(fit_mi_lcs_selfes_hyp2, fit.measures=TRUE, standardized=TRUE, rsquare=F)
```

Results summary:
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5

# model fit
kable(broom::glance(fit_mi_lcs_selfes_hyp2) %>% 
        select(nobs, npar, AIC, BIC, cfi, rmsea, srmr), digits = 3)

# parameters of interest
kable(broom::tidy(fit_mi_lcs_selfes_hyp2, conf.int = FALSE, conf.level = 0.95) %>% 
        select(term, estimate, std.all, statistic, p.value) %>% 
        filter(term %in% c("selfes_t2 ~ selfes_t1", "d_selfes_1 =~ selfes_t2", "d_selfes_1 ~ selfes_t1", # change parameters
                           "d_selfes_1 ~1 ", "selfes_t1 ~1 ", "", # means
                           "d_selfes_1 ~~ d_selfes_1")), digits = 3) # variances
```

::: {.callout-note appearance="minimal"}
Participants increased significantly in self-esteem between the two assessments.
:::

#### Self concept clarity

Fit model:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| output: false
#| cache: true

# Code snippets adapted from Kievit et al. (2018) -- CC-BY -- https://doi.org/10.1016/j.dcn.2017.11.007

# Fit the multiple indicator Univariate Latent Change Score model
mi_lcs_concept_hyp2 <- '
concept_t1 =~ 1*sc01_01_t1 + lamb2*sc01_02_t1 + lamb3*sc01_03_t1 + lamb4*sc01_04_t1 + lamb5*sc01_05_t1 + lamb6*sc01_06_t1 + lamb7*sc01_07_t1 + lamb8*sc01_08_t1 + lamb9*sc01_09_t1 + lamb10*sc01_10_t1 + lamb11*sc01_11_t1 + lamb12*sc01_12_t1 # This specifies the measurement model for concept_t1 
concept_t2 =~ 1*sc01_01_t2 + lamb2*sc01_02_t2 + lamb3*sc01_03_t2 + lamb4*sc01_04_t2 + lamb5*sc01_05_t2 + lamb6*sc01_06_t2 + lamb7*sc01_07_t2 + lamb8*sc01_08_t2 + lamb9*sc01_09_t2 + lamb10*sc01_10_t2 + lamb11*sc01_11_t2 + lamb12*sc01_12_t2 # This specifies the measurement model for concept_t2 with the equality constrained factor loadings

concept_t2 ~ 1*concept_t1     # This parameter regresses concept_t2 perfectly on concept_t1
d_concept_1 =~ 1*concept_t2   # This defines the latent change score factor as measured perfectly by scores on concept_t2
concept_t2 ~ 0*1              # This line constrains the intercept of concept_t2 to 0
concept_t2 ~~ 0*concept_t2    # This fixes the variance of concept_t2 to 0

d_concept_1 ~ 1              # This estimates the intercept of the change score 
concept_t1 ~ 1               # This estimates the intercept of concept_t1 
d_concept_1 ~~ d_concept_1   # This estimates the variance of the change scores 
concept_t1 ~~ concept_t1     # This estimates the variance of the concept_t1 
d_concept_1 ~ concept_t1     # This estimates the self-feedback parameter

sc01_01_t1 ~~ sc01_01_t2   # This allows residual covariance on indicator X1 across T1 and T2
sc01_02_t1 ~~ sc01_02_t2   # This allows residual covariance on indicator X2 across T1 and T2
sc01_03_t1 ~~ sc01_03_t2   # This allows residual covariance on indicator X3 across T1 and T2
sc01_04_t1 ~~ sc01_04_t2   # This allows residual covariance on indicator X4 across T1 and T2
sc01_05_t1 ~~ sc01_05_t2   # This allows residual covariance on indicator X5 across T1 and T2
sc01_06_t1 ~~ sc01_06_t2   # This allows residual covariance on indicator X6 across T1 and T2
sc01_07_t1 ~~ sc01_07_t2   # This allows residual covariance on indicator X7 across T1 and T2
sc01_08_t1 ~~ sc01_08_t2   # This allows residual covariance on indicator X8 across T1 and T2
sc01_09_t1 ~~ sc01_09_t2   # This allows residual covariance on indicator X9 across T1 and T2
sc01_10_t1 ~~ sc01_10_t2   # This allows residual covariance on indicator X10 across T1 and T2
sc01_11_t1 ~~ sc01_11_t2   # This allows residual covariance on indicator X11 across T1 and T2
sc01_12_t1 ~~ sc01_12_t2   # This allows residual covariance on indicator X12 across T1 and T2

sc01_01_t1 ~~ res1*sc01_01_t1   # This allows residual variance on indicator X1 at T1 
sc01_02_t1 ~~ res2*sc01_02_t1   # This allows residual variance on indicator X2 at T1
sc01_03_t1 ~~ res3*sc01_03_t1   # This allows residual variance on indicator X3 at T1
sc01_04_t1 ~~ res4*sc01_04_t1   # This allows residual variance on indicator X4 at T1
sc01_05_t1 ~~ res5*sc01_05_t1   # This allows residual variance on indicator X5 at T1
sc01_06_t1 ~~ res6*sc01_06_t1   # This allows residual variance on indicator X6 at T1 
sc01_07_t1 ~~ res7*sc01_07_t1   # This allows residual variance on indicator X7 at T1
sc01_08_t1 ~~ res8*sc01_08_t1   # This allows residual variance on indicator X8 at T1
sc01_09_t1 ~~ res9*sc01_09_t1   # This allows residual variance on indicator X9 at T1
sc01_10_t1 ~~ res10*sc01_10_t1  # This allows residual variance on indicator X10 at T1
sc01_11_t1 ~~ res10*sc01_11_t1  # This allows residual variance on indicator X11 at T1
sc01_12_t1 ~~ res10*sc01_12_t1  # This allows residual variance on indicator X12 at T1

sc01_01_t2 ~~ res1*sc01_01_t2  # This allows residual variance on indicator X1 at T2 
sc01_02_t2 ~~ res2*sc01_02_t2  # This allows residual variance on indicator X2 at T2 
sc01_03_t2 ~~ res3*sc01_03_t2  # This allows residual variance on indicator X3 at T2
sc01_04_t2 ~~ res4*sc01_04_t2  # This allows residual variance on indicator X4 at T2
sc01_05_t2 ~~ res5*sc01_05_t2  # This allows residual variance on indicator X5 at T2
sc01_06_t2 ~~ res6*sc01_06_t2  # This allows residual variance on indicator X6 at T2 
sc01_07_t2 ~~ res7*sc01_07_t2  # This allows residual variance on indicator X7 at T2 
sc01_08_t2 ~~ res8*sc01_08_t2  # This allows residual variance on indicator X8 at T2
sc01_09_t2 ~~ res9*sc01_09_t2  # This allows residual variance on indicator X9 at T2
sc01_10_t2 ~~ res10*sc01_10_t2 # This allows residual variance on indicator X10 at T2
sc01_11_t2 ~~ res10*sc01_11_t2 # This allows residual variance on indicator X11 at T2
sc01_12_t2 ~~ res10*sc01_12_t2 # This allows residual variance on indicator X12 at T2

sc01_01_t1 ~ 0*1      # This constrains the intercept of X1 to 0 at T1
sc01_02_t1 ~ m2*1     # This estimates the intercept of X2 at T1
sc01_03_t1 ~ m3*1     # This estimates the intercept of X3 at T1
sc01_04_t1 ~ m4*1     # This estimates the intercept of X4 at T1
sc01_05_t1 ~ m5*1     # This estimates the intercept of X5 at T1
sc01_06_t1 ~ m6*1     # This estimates the intercept of X6 at T1
sc01_07_t1 ~ m7*1     # This estimates the intercept of X7 at T1
sc01_08_t1 ~ m8*1     # This estimates the intercept of X8 at T1
sc01_09_t1 ~ m9*1     # This estimates the intercept of X9 at T1
sc01_10_t1 ~ m10*1    # This estimates the intercept of X10 at T1
sc01_11_t1 ~ m11*1    # This estimates the intercept of X11 at T1
sc01_12_t1 ~ m12*1    # This estimates the intercept of X12 at T1

sc01_01_t2 ~ 0*1      # This constrains the intercept of X1 to 0 at T2
sc01_02_t2 ~ m2*1     # This estimates the intercept of X2 at T2
sc01_03_t2 ~ m3*1     # This estimates the intercept of X3 at T2
sc01_04_t2 ~ m4*1     # This estimates the intercept of X4 at T2
sc01_05_t2 ~ m5*1     # This estimates the intercept of X5 at T2
sc01_06_t2 ~ m6*1     # This estimates the intercept of X6 at T2
sc01_07_t2 ~ m7*1     # This estimates the intercept of X7 at T2
sc01_08_t2 ~ m8*1     # This estimates the intercept of X8 at T2
sc01_09_t2 ~ m9*1     # This estimates the intercept of X9 at T2
sc01_10_t2 ~ m10*1    # This estimates the intercept of X10 at T2
sc01_11_t2 ~ m11*1    # This estimates the intercept of X11 at T2
sc01_12_t2 ~ m12*1    # This estimates the intercept of X12 at T2
'
fit_mi_lcs_concept_hyp2 <- lavaan(mi_lcs_concept_hyp2, data=df_sbsa_wide_wb, estimator='mlr', fixed.x=FALSE, missing='fiml')
summary(fit_mi_lcs_concept_hyp2, fit.measures=TRUE, standardized=TRUE, rsquare=F)
```

Results summary:
```{r}
#| echo: true
#| fig-width: 9.5
#| fig-height: 6.5

# model fit
kable(broom::glance(fit_mi_lcs_concept_hyp2) %>% 
        select(nobs, npar, AIC, BIC, cfi, rmsea, srmr), digits = 3)

# parameters of interest
kable(broom::tidy(fit_mi_lcs_concept_hyp2, conf.int = FALSE, conf.level = 0.95) %>% 
        select(term, estimate, std.all, statistic, p.value) %>% 
        filter(term %in% c("concept_t2 ~ concept_t1", "d_concept_1 =~ concept_t2", "d_concept_1 ~ concept_t1", # change parameters
                           "d_concept_1 ~1 ", "concept_t1 ~1 ", "", # means
                           "d_concept_1 ~~ d_concept_1")), digits = 3) # variances
```

::: {.callout-note appearance="minimal"}
Self concept clarity improved significantly across time.
:::

### Hypothesis 3: Distance between ideal- and current-self over time {#hyp3}

*The distance between ideal- and current-self will decrease in both groups.* 

We will use two strategies to test this hypothesis. First, we will compute the Fisher z-transformed profile correlation between current- and ideal-self and test whether it increased across assessments. Second, we will test whether the squared difference between current- and ideal-self ratings for each Big Five trait decreased across assessments. We will test mean-level differences in profile correlations and squared differences between baseline and follow up using repeated-measures t-test.

#### Profile similarity

Reshape to wide:
```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"

# reshape to wide
df_sbsa_wide_profdiff <- df_sbsa %>% 
  arrange(pid, time) %>% 
  select(pid, time, profile_corr_item_z, profile_corr_facet_z, ends_with("_sqdiff")) %>% 
  pivot_wider(names_from = time,
              names_sep = "_t",
              values_from = -c(pid, time))
```

Checking assumptions
```{r}
#| echo: true
# item-level profile correlation
shapiro.test(df_sbsa_wide_profdiff$profile_corr_item_z_t2 - df_sbsa_wide_profdiff$profile_corr_item_z_t1) 
lillie.test(df_sbsa_wide_profdiff$profile_corr_item_z_t2 - df_sbsa_wide_profdiff$profile_corr_item_z_t1)

# descriptives
psych::describe(df_sbsa_wide_profdiff$profile_corr_item_z_t1)
psych::describe(df_sbsa_wide_profdiff$profile_corr_item_z_t2)

# facet-level profile correlation
shapiro.test(df_sbsa_wide_profdiff$profile_corr_facet_z_t2 - df_sbsa_wide_profdiff$profile_corr_facet_z_t1) 
lillie.test(df_sbsa_wide_profdiff$profile_corr_facet_z_t2 - df_sbsa_wide_profdiff$profile_corr_facet_z_t1)

# descriptives
psych::describe(df_sbsa_wide_profdiff$profile_corr_facet_z_t1)
psych::describe(df_sbsa_wide_profdiff$profile_corr_facet_z_t2)
```

Results summary:
```{r}
#| echo: true
#| warning: false
t_profile_corr_item <- t.test(df_sbsa_wide_profdiff$profile_corr_item_z_t2, df_sbsa_wide_profdiff$profile_corr_item_z_t1, paired = TRUE)
t_profile_corr_facet <- t.test(df_sbsa_wide_profdiff$profile_corr_facet_z_t2, df_sbsa_wide_profdiff$profile_corr_facet_z_t1, paired = TRUE)

kable(bind_rows(tidy(t_profile_corr_item), tidy(t_profile_corr_facet)) %>% mutate(outcome = c("Item-level profile corr.", "Facet-level profile corr.")) %>% select(outcome, everything()), digits = 3)

# effect sizes
d_profile_corr_item <- psych::cohen.d(profile_corr_item_z ~ time, data = df_sbsa)
d_profile_corr_item$cohen.d
d_profile_corr_facet <- psych::cohen.d(profile_corr_facet_z ~ time, data = df_sbsa)
d_profile_corr_facet$cohen.d
```

Plot 
```{r}
#| echo: true
#| warning: false
#| fig-width: 9.5
#| fig-height: 6.5
profile_df_plot <- df_sbsa %>% select(pid, time, profile_corr_item_z, profile_corr_facet_z) %>% 
  pivot_longer(-c(pid, time), names_to = "itemfacet", values_to = "corr") %>% 
  mutate(itemfacet2 = fct_recode(itemfacet, "Item-level" = "profile_corr_item_z", "Facet-level" = "profile_corr_facet_z"),
         itemfacet2 = fct_reorder(itemfacet2, corr, .desc = F))

ggplot(profile_df_plot) + 
  aes(x = as.factor(time), y = corr) + 
  geom_boxplot() + 
  geom_violin(fill = NA) +
  facet_wrap(vars(itemfacet2)) +
  labs(x = "Measurement Occasion", y = "Profile correlation", 
       title = "Hypothesis 3: Distance between ideal- and current-self") + 
  theme_bw()
```

::: {.callout-note appearance="minimal"}
Significantly higher profile correlations at the second measurement occasion, both for the item-level profile correlation and the facet-level profile correlations.
:::

#### Individual traits: squared differences

Checking assumptions
```{r}
#| echo: true

# extra
shapiro.test(df_sbsa_wide_profdiff$extra_sqdiff_t2 - df_sbsa_wide_profdiff$extra_sqdiff_t1) 
lillie.test(df_sbsa_wide_profdiff$extra_sqdiff_t2 - df_sbsa_wide_profdiff$extra_sqdiff_t1)
# descriptives
psych::describe(df_sbsa_wide_profdiff$extra_sqdiff_t1)
psych::describe(df_sbsa_wide_profdiff$extra_sqdiff_t2)

# agree
shapiro.test(df_sbsa_wide_profdiff$agree_sqdiff_t2 - df_sbsa_wide_profdiff$agree_sqdiff_t1) 
lillie.test(df_sbsa_wide_profdiff$agree_sqdiff_t2 - df_sbsa_wide_profdiff$agree_sqdiff_t1)
# descriptives
psych::describe(df_sbsa_wide_profdiff$agree_sqdiff_t1)
psych::describe(df_sbsa_wide_profdiff$agree_sqdiff_t2)

# consc
shapiro.test(df_sbsa_wide_profdiff$consc_sqdiff_t2 - df_sbsa_wide_profdiff$consc_sqdiff_t1) 
lillie.test(df_sbsa_wide_profdiff$consc_sqdiff_t2 - df_sbsa_wide_profdiff$consc_sqdiff_t1)
# descriptives
psych::describe(df_sbsa_wide_profdiff$consc_sqdiff_t1)
psych::describe(df_sbsa_wide_profdiff$consc_sqdiff_t2)

# neuro
shapiro.test(df_sbsa_wide_profdiff$neuro_sqdiff_t2 - df_sbsa_wide_profdiff$neuro_sqdiff_t1) 
lillie.test(df_sbsa_wide_profdiff$neuro_sqdiff_t2 - df_sbsa_wide_profdiff$neuro_sqdiff_t1)
# descriptives
psych::describe(df_sbsa_wide_profdiff$neuro_sqdiff_t1)
psych::describe(df_sbsa_wide_profdiff$neuro_sqdiff_t2)

# openn
shapiro.test(df_sbsa_wide_profdiff$openn_sqdiff_t2 - df_sbsa_wide_profdiff$openn_sqdiff_t1) 
lillie.test(df_sbsa_wide_profdiff$openn_sqdiff_t2 - df_sbsa_wide_profdiff$openn_sqdiff_t1)
# descriptives
psych::describe(df_sbsa_wide_profdiff$openn_sqdiff_t1)
psych::describe(df_sbsa_wide_profdiff$openn_sqdiff_t2)
```

Results summary:
```{r}
#| echo: true
#| warning: false
mod_traits_sqdiff <- df_sbsa_wide_profdiff %>% 
  select(-starts_with("profile")) %>% 
  pivot_longer(-c(pid), 
               names_to = c("test", "time"), values_to = "score", 
               names_pattern = "(.*)_(t1|t2)") %>% 
  filter(!is.na(score)) %>% 
  group_by(pid, test) %>% 
  mutate(assessments = n()) %>% 
  ungroup() %>% 
  filter(assessments==2) %>% 
  select(-assessments) %>% 
  group_nest(test) %>% 
  mutate(t_tests = map(data, ~t.test(score ~ time, data = .x, paired = TRUE))) %>% 
  pull(t_tests) %>% 
  purrr::set_names(names(b5_vars))

mod_traits_unlist <- mod_traits_sqdiff[[1]] %>% tidy()
for (i in 2:length(mod_traits_sqdiff)) {
  mod_traits_unlist <- bind_rows(mod_traits_unlist, mod_traits_sqdiff[[i]] %>% tidy())
}

kable(mod_traits_unlist %>% mutate(outcome = names(b5_vars)) %>% select(outcome, everything()), digits = 3)

# effect sizes
cohend_cust = function(outcome, df) {
  form = as.formula(paste0(outcome, " ~ time"))
  psych::cohen.d(form, data = df)
}

d_trait <- cohend_cust(paste0(str_trunc(names(b5_vars)[1], 5, ellipsis = ""), "_sqdiff"), df_sbsa)
d_traits_unlist <- as_tibble(d_trait$cohen.d)
for (i in 2:length(names(b5_vars))) {
  d_trait <- cohend_cust(paste0(str_trunc(names(b5_vars)[i], 5, ellipsis = ""), "_sqdiff"), df_sbsa)
  d_traits_unlist <- bind_rows(d_traits_unlist, as_tibble(d_trait$cohen.d))
}
kable(d_traits_unlist %>% mutate(outcome = names(b5_vars)) %>% select(outcome, everything()), digits = 3)
```

::: {.callout-note appearance="minimal"}
Significantly lower squared mean-level differences at the second measurement occasion, both for the Big Five traits and the 15 BFI-2 facets.
:::

Plot (traits/facets sorted by average size of squared differences)
```{r}
#| echo: true
#| warning: false
#| fig-width: 9.5
#| fig-height: 4.5
sqdiff_df_plot <- df_sbsa %>% 
  select(pid, time, all_of(paste0(str_trunc(names(b5_vars), 5, ellipsis = ""), "_sqdiff"))) %>% 
  pivot_longer(-c(pid, time), names_to = "trait", values_to = "sqdiff") %>% 
  group_by(trait) %>% 
  mutate(cur_group_id()) %>% 
  ungroup() %>% 
  mutate(trait2 = fct_recode(trait, !!! setNames(paste0(str_trunc(names(b5_vars), 5, ellipsis = ""), "_sqdiff"),
                                                 str_to_title(names(b5_vars)))),
         trait2 = fct_reorder(trait2, sqdiff, .desc = T))

plot_sqdiff <- ggplot(sqdiff_df_plot) + 
  aes(x = as.factor(time), y = sqdiff) + 
  geom_boxplot() + 
  geom_violin(fill = NA) +
  ggforce::facet_wrap_paginate(~trait2, ncol=3, nrow=2) +
  labs(x = "Measurement Occasion", y = "Squared difference") + 
  theme_bw()

plot_sqdiff + ggforce::facet_wrap_paginate(~trait2, ncol=4, nrow=1, page = 1)
plot_sqdiff + ggforce::facet_wrap_paginate(~trait2, ncol=4, nrow=1, page = 2)
plot_sqdiff + ggforce::facet_wrap_paginate(~trait2, ncol=4, nrow=1, page = 3)
plot_sqdiff + ggforce::facet_wrap_paginate(~trait2, ncol=4, nrow=1, page = 4)
plot_sqdiff + ggforce::facet_wrap_paginate(~trait2, ncol=4, nrow=1, page = 5)
```

::: {.callout-note appearance="minimal"}
For some of the facets, the distribution look very similar and differences over time are perhaps driven by a few outliers.
:::


<!--
## References

::: {#refs}
:::
-->